In order to clarify the expected functionality of the system, in this
subsection we propose several possible scenarios. In each scenario
we emphasize several specific interactions between the users and the
system, but, in some of them, we do not describe the entire process
carried out interacting with TS to avoid useless repetitions.


\subsubsection{Scenario 1}

Bob is an unregistered passenger of TS. He has decided to visit a
friend that lives in another district. He accesses the TS using the
PWA via browser installed on his PC, he specifies his current address
because his PC can’t provide him with browser geolocalization. After
accepting terms and conditions related to the service he confirms
the request. The TS system processes his request and sends a notification
to Bob. Meanwhile the system sends the request to the first available
taxi in the queue associated to the area where Bob is. The taxi driver,
Tom, after having received the request on his smartphone via TMA,
he confirms it. Tom visualizes the request information details and
leaves from his location to get to the address specified by Bob. TS
system calculates the waiting time and shows it to Bob. When Tom arrives
to Bob's, he picks up him and brings him to his friend. Before leaving
Bob pays Tom for the service and Tom informs the system that he is
available again.


\subsubsection{Scenario 2}

As soon as Alice left the theater it started raining, so she decided
to try TS service for the first time. She uses her 3G connection to
download the PMA and starts it. After that she accepts terms and conditions
of TS, the system retrieves Alice’s current position by means of her
GPS. She confirms the requests and the system contacts the first taxi
available in her zone. Unfortunately it has run out of fuel so, Tim,
the taxi driver is waiting his turn at the gas station and decides
to refuse the request. The system puts the Tim’s taxi at the end of
the queue and sends a request at the second taxi available. Tess,
the new taxi driver, accepts the request, picks up Alice and brings
her to home.


\subsubsection{Scenario 3}

Robb needs to reach the university campus because he has to addend
Software Engineering 2 morning class, so he reaches the bus stop but
he notices a sign informing that an unexpected public transportation
strike is going on. Unfortunately this happens quite often, that's
why Robb is a registered passenger of TS. He logs in the PMA and requests
a taxi. Due to the strike a large number of requests has been forwarded
the system so no taxi is available at the moment in that zone of the
city. Therefore the first taxi in the queue of an adjacent zone is
contacted. The taxi driver, Taylor, accepts the request. The system
shows the expected waiting time on Rob's smartphone. After 15 minutes
Taylor picks up Robb who will get to university, in time for the class.


\subsubsection{Scenario 4}

Arya booked a low cost flight to Marrakesh but the plane leaves early
in the morning so she decided to register on TS website to reserve
a taxi. She filled the registration form with the requested information
and confirmed, accepting terms and conditions. The system sends her
a confirmation e-mail. A few days before the departure she logs in
her personal area on the PWA and reserves a taxi, specifying her address
and the meeting time. The leaving day she hasn't heard the alarm clock
and she hasn't woken up. When Takashi, the taxi driver, arrives at
Arya’s place he doesn’t find anyone so he waits for 10 minutes and
then informs the system. The system puts Takashi's taxi at the end
of the available taxi queue.


\subsubsection{Scenario 5}

In the city a huge sport event has been organized for today so the
city center is closed. Jon wants to reach his house after a stressful
working day. Jon usually comes back home using public transportation
but today it's a mess so he decides to take a taxi. He sends a request
using his PMA but all the taxis in all the zones are busy due to the
unexpected number of people coming to attend the event. The system
informs Jon about the situation and provides Jon with the expected
waiting time: one hour, too much for Jon. So he decides to ask one
of his colleagues for a lift.


\subsubsection{Scenario 6}

Sansa always uses taxis to move in the city because she has never
passed her driving license exam. Today she needs a taxi to reach the
shopping center but unfortunately she doesn't have access to the Internet
so she calls the taxi service phone number. A call center operator,
Trudy, answers the phone and asks the location where the taxi should
pick up her and the number of passengers. Sansa tells him her current
address and says she would be the only passenger. Trudy uses a PWA
to send a request to the TS system and announce to Sansa the expected
waiting time when she receives the confirmation by TS. 
