
\subsection{External Interface Requirements }

\input{\string"specific-requirements/3.1-external-interface-requirements/external interface requirements.tex\string"}

\clearpage{}


\subsection{Functional Requirements }

\input{\string"specific-requirements/3.2-functional-requirements/functional requirements.tex\string"}

\clearpage{}


\subsection{Scenarios}

\input{specific-requirements/3.3-scenarios/scenarios.tex}

\clearpage{}

\input{\string"specific-requirements/3.4-use-cases/use case.tex\string"}

\clearpage{}

\input{\string"specific-requirements/3.6-other-uml/class diagram and other.tex\string"}

\clearpage{}


\subsection{Non functional requirements}

Since TS system is intended to increase the degree of usability of
the taxi service and perform improvements in the available taxi queue
management, according to stackeholders' expectations we identified
the following non functional requirements.


\subsubsection{Performance}
\begin{itemize}
\item All internal elaborations carried out by QMA must have a response
time of 100 ms in 99\% of times.
\item TMA, PMA and PWA must have a response time of 10 ms in 99\% of times
for local elaborations (not involving Internet connection).
\item Remote interaction (via Internet) within TS system must least at most
2 seconds otherwise the connection is closed.
\item TS system shall support at least 500 simultaneous connections.
\end{itemize}

\subsubsection{Reliability}
\begin{itemize}
\item TS system shall ensure that every operation coming from TMA, PMA and
PWA is correctly processed.
\item All the user inputs are verified by the local application before being
sent to the TS system .
\item TS system shall be a transactional system (both operations generated
by users and internal operations carried out by TS system are transactions).
\end{itemize}

\subsubsection{Availability }
\begin{itemize}
\item The TS system must be available 99.9\%. 
\item A hardware duplicate must be ready to be activated when maintenance
is performed or failure occurs to ensure continuity of the service.
\item A backup of data should be performed every week to prevent any loss
of data in the TS system.
\end{itemize}

\subsubsection{Security }
\begin{itemize}
\item All sensitive data collected from users must be stored in safe devices
accessible only by authorized users to prevent loss, manipulation
or stealing.
\item All data flowing between system and users must be encrypted to ensure
confidentiality.
\item Registered passenger's password must be changed every three months.
\end{itemize}

\subsubsection{Maintainability }
\begin{itemize}
\item TS system shall be developed in order to reduce the maintenance cost,
trying to anticipate and preventing future interventions (corrective
and adaptive maintenance) by means of standard patterns (in particular
the architecture must follow the MVC pattern).
\item TS system shall expose a set of APIs in order to allow future functionalists
extensions (perfective maintenance).
\item Thanks to hardware duplication, hardware maintenance interventions
will be performed without service interruption.
\end{itemize}

\subsubsection{Portability }
\begin{itemize}
\item TMA and PMA shall be installable in both iOS, Android and Windows
mobile.
\item PWA shall be accessible by means of all up to date browsers having
cookies enabled.
\end{itemize}

\subsubsection{Documentation}
\begin{itemize}
\item An accurate user guide must be available online.
\item All the documents produced during the design and development of the
TS shall be available for specialized personnel.
\end{itemize}

\subsubsection{User interface and human factors }
\begin{itemize}
\item TS is meant for user without any particular knowledge or experience
in the field of IT so the application must be intuitive and easy to
master.
\item Every functionality shall be reached surfing no more than 4 pages.\end{itemize}

